\Large {\bf rt1d: User's Manual}

### 2011-12-14 doc/manual/rt1d_manual.tex
Everything good for the paper?

>>>>

%%% 
%% Troubleshooting
%%%
\section{Troubleshooting}
If your results look horribly, horribly wrong, here are a few places where you could've gone wrong.  We'll start with things that may occur with the stable version of the code.

Now, if you modify or add anything in the source code (awesome by the way!), you're far more likely to encounter troubles.

\begin{description}
    \item[Totally Bogus Results] This is will almost certainly happen at some point in the development process. But, if it happens even after you're \textit{positive} the error was fixed, my guess is that you are using the integral tables that were generated with the previous, error-ridden version of the code.  Try removing the integral tables and re-running your simulation.
\end{description}
